### 2016-10-27 paper/intro.tex

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.  We
understand that the alternative of renting server farms (or even
building one) to mitigate the regression testing problem is a
potential escape for large IT organizations but not as attractive for
open-source projects and projects from smaller organizations with
lower budgets for building testing infrastructures.  This paper
studies (1) how relevant the problem of long-running test suites in
open-source software is, (2) what are the causes of high execution
cost (CPU vs. IO), and (3) what is the impact of existing open-source
sound approaches to reducing cost.

>>>>

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.  We
understand that the alternative of renting server farms (or even
building one) to mitigate the regression testing problem is a
potential escape for large IT organizations but not as attractive for
open-source projects and projects from smaller organizations with
lower budgets for building testing infrastructures.  As such, this
paper studies (1) how relevant the problem of long-running test suites
in open-source software really is, (2) what are the causes of high
execution costs (\eg{}, IO or CPU), and (3) what is the impact of
existing open-source sound approaches to reducing cost.
